---
title: "R Notebook"
output: html_notebook
---

```{r}
library('tidyverse')
```

1. Read in `districts.csv` into a tibble named `districts`.

```{r}
districts <- read_csv('../data/districts.csv')
```

2. Notice that the first row corresponds to the whole State of Tennessee. Remove this row and save the result back to `districts`.

```{r}
districts <- districts[-c(1),]
```

3. How many districts have a proficiency rate of at least 80% for both alg_1 and eng_1?

BEST answer:
```{r}
districts |> 
  filter(alg_1 >= 80, eng_1 >= 80) |> 
  nrow()
```

Other ways:
```{r}
districts |>
  filter(alg_1 >= 80, eng_1 >= 80)
```
```{r}
districts |> 
  count(alg_1 >= 80, eng_1 >= 80)
```

4. How many districts have a proficiency rate less than 50% for either alg_1 or eng_1?

```{r}
districts |> 
  filter(alg_1 < 50 | eng_1 < 50) |> 
  nrow()
```

```{r}
districts |> 
  filter(alg_1 < 50 | eng_1 < 50)
```

5. Which district has the lowest graduation rate?

```{r}
districts |> 
  select(region, grad) |> 
  arrange(grad) |> 
  head(1)
```

```{r}
districts |> 
  select(system_name, grad) |> 
  arrange(grad) |> 
  head(1)
```


6. Within the Mid Cumberland region, which district has the highest ACT composite?

```{r}
districts |> 
  filter(region == "Mid Cumberland") |> 
  select(system_name, act_composite) |> 
  arrange(desc(act_composite)) |> 
  head(1)
```

7. Create a scatter plot to compare alg_1 proficiency rates to alg_2 rates. What do you notice? Facet this plot by region. Does anything stand out when you facet the plots?

```{r}
districts |> 
  ggplot(aes(x = alg_1, y = alg_2)) + geom_point()
```

It seems that there is a strong positive linear relationship between algebra 1 and 2 proficiency rates. 

```{r}
districts |> 
  ggplot(aes(x = alg_1, y = alg_2)) + geom_point() + facet_wrap(~region)
```

Observations: Some districts seems to have a better proficiency than the rest. Notable districts are Southwest/Memphis, First TN, and South Central. Southeast and Upper Cumberland districts seem to have poorer relationships. 

8. When creating this bar chart you may have noticed that some districts have missing enrollment values. For how many districts is this the case?


```{r}
districts |> 
  filter(is.na(enrollment)) |> 
  nrow()
```

9. A lot of rows are missing additional values. Which district has the largest number of missing values (across all variables)? Hint: you might want to look at rowwise and c_across to answer this question.

BEST answer: 

```{r}
districts |> 
  mutate(count_na = rowSums(is.na(districts))) |> 
  arrange(desc(count_na)) |> 
  select(system_name, count_na) |> 
  head(1)
```

```{r}
na_test <- districts[rowSums(is.na(districts))> 0,] 
```

10. What is the mean graduation rate across all districts? What might be wrong with using just the regular mean to assess average graduation rates?

11. Redo the previous question but use a weighted average (`weighted.mean`) graduation across all districts, weighing by enrollment. How much does this change your answer? Can you explain using the data the reason for the big change from using the mean?

12. Find the unweighted and weighted average graduation rate by district.